---
name: Stephanie Kobakian
qualifications: BCom, BEco
email: srkobakian@outlook.com
github: srkobakian
phone: 0433 699 797
headcolor: "165331"
aboutme: ""
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::moderncv:
    theme: casual
---

```{r setup, include=FALSE}
library(vitae)
library(tibble)
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE,
                      message = FALSE)
```

A critical thinker and engaged collaborator delivering business insights. I am dedicated to solving problems, using data analysis and visualisation to develop and  effectively communicate data driven solutions.


# Technical Skills

- **Programming:** R, LaTex, SQL and python
- **Data science:** web scraping, data collection, analytics and visualisation
- **Software Development:** collaborative version control and continuous integration
- **Communication:** conference presentations, reports for commercial and non-profits


<!-- Prof. Kerrie Mengersen, Prof. Dianne Cook, Dr. Earl Duncan -->


# Education 

```{r education}
tribble(
  ~ when,
  ~ what,
  ~ where,
  ~ with,
  ~ why,
  "2018 - 2020",
  "Master of Philosophy (Statistics)",
  "Brisbane, Australia",
  "Queensland University of Technology",
  "A New Algorithm For Effectively Visualising Australian Spatio-Temporal Disease Data",
  
  "2014 - 2017",
  "Bachelor of Commerce and Bachelor of Economics",
  "Melbourne, Australia",
  "Monash University",
  "Majors: Econometrics and Business Modelling",
) %>% 
  brief_entries(
    glue::glue("\\textbf{<what>} \\newline \\textit{<with>}, <where>  \\newline \\small{<why>}",
               .open = "<", .close = ">"), when, .protect = FALSE)
# %>% 
# detailed_entries(when = when,
#                  what = what,
#                  where = where,
#                  with = with,
#                  why = why)
```


# Experience

```{r work}
tribble(
  ~ what, 
  ~ when, 
  ~ with, 
  ~ where, 
  ~ why,
  "Lead Data Scientist",
  "Jan. 2019 - Present",
  "WhyHive",
  "Remote",
  c(
    "Use R to manage data, perform high quality data cleaning, conduct statistical analysis, modelling and generate data visualisations",
    "Create and present analytical findings in written and visual data driven research reports and presentations",
    "Perform program evaluation and use evidence to measure and report on outcomes"
    ), 
  
  "Editorial Assistant for the R Journal",
  "Jan. 2019 - Present",
  "R Consortium",
  "",
  c("Proofread submissions for issue publication",
    "Plan projects and set milestones to ensure objectives are achieved",
    "Evaulate the shifting priorities of various stakeholders and adapt projects accordingly",
    "Liase with team memebers to plan and negotiate targets",
    "Write R functions to automate checks of submissions"),
 
  "Research assistant to Prof. Dianne Cook",
  "Jan. 2016 - Present",
  "Monash University",
  "Clayton",
  c("Create and effectively manage project priorities",
    "Manage hours and priorities to acheive project deadlines",
    "Develop an R package to create Shiny Applications that produce tidy data sets from image based surveys"),
  
  ) %>% 
detailed_entries(what, 
                 when, 
                 with, 
                 where, 
                 why)


## internship
# tribble(
#   ~ what,
#   ~ with,
#   ~ where,
#   ~ when,
#   ~ why,
#   "Intern",
#   "Tennis Australia: Game Insight Group",
#   "Melbourne, Australia",
#   "2017",
#   "Work Integrated Learning Intern to Dr. Stephanie Kovalchik, Senior Sport Scientist."
# ) %>% 
# detailed_entries(what, 
#                  when, 
#                  with, 
#                  where, 
#                  why)

# Notable press mentions:
# https://www.afr.com/companies/sport/facial-recognition-technology-comes-to-tennis-to-track-player-emotions-20180118-h0k7go
# https://www2.monash.edu/impact/articles/econometrics/no-more-poker-face-facial-recognition-could-change-how-we-view-tennis/

```


```{r teachexp} 
# Experience

#My teaching quality at Monash University has been consistently recognised with positive student evaluations and individual praise from my students.
#In addition to sessional teaching, I have taught data analysis skills and R to high school students at Monash workshops.


## Teaching
tribble(
  ~ what,
  ~ uni,
  ~ campus,
  ~ when,
  ~ why,
  "Teaching associate",
  "Monash University",
  "Clayton, Australia",
  "",
  c(
  "ETC1010: Introduction to data analysis, 2018 - 2020",
  "ETC5510: Introduction to data analysis, S1 2020",
  "ETC5513: Collaborative and reproducible practices, S1 2020",
  "ETC5512: Wild-caught data, S1 2020",
  "ETX2250: Data Visualisation and Analytics, Summer 2017")
) %>% 
  detailed_entries(what, when, uni, campus, why)

```

# Publication

```{r software}
bibliography_entries("publications.bib")
```

# Authored Software

```{r}
## pkgs
tribble(
  ~ pkg,
  ~ when,
  ~ what,
  ~ why,
  ~ details,
  "sugarbag",
  "2019",
  "Author",
  "Kobakian, Stephanie. 2018. sugarbag: Create Tessellated Hexagon Maps of Australia.",
  "Each polygon is represented by a hexagon tile, placed as close to it's original centroid as possible, with a focus on maintaining spatial relationship to a focal point",
  "taipan",
  "2018",
  "Author",
  "Kobakian, Stephanie and O'Hara-Wild, Mitchell. 2017. taipan: Tool for Annotating Images in Preparation for Analysis.",
  "Generates shiny apps for annotating images, these annotations are typically used for training and evaluating machine learning models"
) %>%
  brief_entries(
    glue::glue(
      "\\textbf{<pkg>}: <what>. <why> <details>",
      .open = "<",
      .close = ">"
    ),
    when,
    .protect = FALSE
  )

```

# Presentations

```{r}
## Talks
tribble(
  ~ when,
  ~ title,
  ~ why,
  ~ with,
  "2019",
  "An Australian alternative to choropleth maps; visualising geo-spatial disease data",
  "Alternative map displays for presenting spatial distributions in Australia",
  "WOMBAT 2019",
  #"https://srkobakian-wombat19.netlify.app",
  
  "2019",
  "An Australian alternative to choropleth maps; visualising geo-spatial disease data",
  "Alternative map displays for presenting spatial distributions in Australia",
  "Masters symposium, Queensland University of Technology",
  #"https://srkobakian-qut.netlify.app",
  "2019",
  "Maps, hexagons and life in Australia",
  "An algorithm to create tesselated hexagon tile maps for Australia",
  "Young Statisticians Conference 2019",
  #"https://srkobakian-ysc.netlify.app",
  "2019",
  "Taipan: Woman Faces Machine",
  "Storing information from images",
  "useR!2018",
  #"https://srkobakian-user2018.netlify.app",
  "2018",
  "Tidy data structures and image analysis",
  "A real example of tidy data creation, highlighting the differences between variables and observations",
  "ETX2250 Data Visualisation and Analytics",
  #"https://srkobakian-medascin.netlify.app",
  # "2017",
  # "Facial Recognition",
  # "Emotions in tennis",
  # "Tennis Australia",
  # #"https://srkobakian-ta.netlify.app",
  # 
  "2017",
  "Sports Analytics",
  "Emotions in tennis",
  "Wombat MeDaScIn",
  #"https://srkobakian-medascin.netlify.app"
) %>%
  brief_entries(when = when, glue::glue(
    "\\textit{<title>:} <why>. <with>",
    .open = "<",
    .close = ">"
  ), .protect = FALSE)

```


# Awards

```{r}
tribble(
  ~ what,
  ~ when,
  ~ where,
  ~ with,
  ~ why,
  "Championship Team",
  "2018",
  "Atlas of Living Australia",
  "UseR!2018 Datathon",
  "A Shiny app to aid in the exploration of animals in Australia. Displaying sightings of bee species across Australia in a colourful and interactive application.",
  
  "Championship Team",
  "2016",
  "SAP University Alliances",
  "Analytics Competition",
  "Created an infographic presenting the state of homelessness in Australia. Recommended solutions to address the drivers of homelessness for various age groups.",
  
  "Scholarship Awardee and Internship",
  "2016",
  "Dep. of Econometrics and Business Statistics",
  "Monash Winter Research Program",
  "Worked under Dr Stephanie Kovalchik and Prof. Dianne Cook to begin a research project within the Game Insight Group to analyse the emotional experience of elite tennis players and develop statistics to incorporate in the television coverage of the Australian Open. Applying the facial recognition software, and performing statistical analyses to determine the performance accuracy."
) %>% 
  detailed_entries(what, when, with, where, why)
```



<!-- ```{r workshops} -->
<!-- # Experience -->
<!-- tribble( -->
<!--   ~ event, -->
<!--   ~ where, -->
<!--   ~ when, -->
<!--   ~ why, -->
<!--   "Big Data Day", -->
<!--   "Monash University", -->
<!--   "2018-Present", -->
<!--   "High school student workshop using R and shiny by Prof Dianne Cook", -->

<!--   "Disease risk modeling and visualization using R", -->
<!--   "UseR!", -->
<!--   "2018", -->
<!--   "One day workshop by Dr Paula Moraga", -->

<!--   "Sports Analytics with R", -->
<!--   "WOMBAT 2017", -->
<!--   "2017", -->
<!--   "3 hour workshop Dr Stephanie Kovalchik", -->
<!--   # <https://github.com/skoval/WOMBATtutorial> -->

<!--   "Visualisation for Data Mining", -->
<!--   "WOMBAT 2017", -->
<!--   "2017", -->
<!--   "3 hour workshop by Prof Dianne Cook and Prof Eun-Kyung Lee"  -->
<!--   # <https://github.com/EK-Lee/WOMBAT-2017> -->
<!-- )  %>%  -->
<!--   detailed_entries(with = event, when = when, where = where, what = why) -->

<!-- ``` -->
